\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-30 paper.tex
Rearrange script folder

To create a smooth \gD{} representation (Figure~\ref{fig-NLDR-scurve}
(d)), it is necessary to remove edges that connect distant bin centroids
in the triangular mesh. These edges only exist in the \gD{} model and do
not extend into \pD{}, so their removal does not impact the model in
\pD{}. Although there are no specific criteria for determining the
benchmark value to remove long edges, the following steps provide an
approach to identifying a suitable threshold:

>>>>

Edges define the neighbourhood structure, in order to provide a smooth
\gD{} representation of the fitted model.
Figure~\ref{fig-scurve-true-sc} shows a wire frame of the true model
that was used to generate the S-curve example data. The fitted model
should come reasonably close to this, if the fitting has been
successful. We don't ever have this, of course

(Figure~\ref{fig-NLDR-scurve} (d)), it is necessary to remove edges that
connect distant bin centroids in the triangular mesh. These edges only
exist in the \gD{} model and do not extend into \pD{}, so their removal
does not impact the model in \pD{}. Although there are no specific
criteria for determining the benchmark value to remove long edges, the
following steps provide an approach to identifying a suitable threshold:
